R Notebook

### 2019-03-13 analysis/INLA/test-INLA-sensor.Rmd
tweak of markdown

```{r}
# alternative to function, hard code
# samples = 10L
# pred_grid <- pg_one_year

@@

```{r prediction-grid-calcs}
attributes(projected)
pg_one_year <- filter(pg, year == min(pg$year))
attributes(projected$latent_grid)
# out <- stats::plogis(p_bin) * exp(p_pos)
out_med <- apply(projected$latent_grid, c(1,3), median)
# out_bin <- stats::plogis(p_bin)
# out_bin <- apply(out_bin, c(1, 3), median)
pg_all <- bind_rows(replicate(dim(projected$latent_grid)[3], pg, simplify = FALSE))
out_long <- reshape2::melt(out_med)
pg_all$time <- out_long$Var2
pg_all$pred <- out_long$value

# pg$year_k <- pg$year - min(pg$year) + 1
# count_k <- unique(year_k)

```{r prediction-grid-calcs}
attributes(projected$spatial_field)
# out <- stats::plogis(p_bin) * exp(p_pos)
out_med_sp <- apply(projected$spatial_field, c(1,3), median)
out_long_sp <- reshape2::melt(out_med_sp)
pg_all$sp_field <- out_long_sp$value
```

@@

  g
}
# make_plot(pg_all)
median(pg_all$pred)

make_plot(pg_all, "pred") + facet_wrap(~ time) +
  scale_fill_gradient2(
    midpoint = median(pg_all$pred),
    low = scales::muted("blue"), 
    mid = "white",
    high = scales::muted("red"))

@@

make_plot(pg_all, "depth_scaled") +
  scale_fill_gradient2(
    midpoint = 0,
    high = scales::muted("blue"), 
    mid = "white",
    low = scales::muted("red"))
```

>>>>

```{r , eval=TRUE, include=FLASE}
# alternative to function, hard code
# samples = 10L
# pred_grid <- pg_one_year

@@

```{r prediction-grid-calcs}
attributes(projected)
pg_one_year <- filter(pg, year == min(pg$year))
attributes(projected$latent_grid)
out_med <- apply(projected$latent_grid, c(1,3), median)
pg_all <- bind_rows(replicate(dim(projected$latent_grid)[3], pg, simplify = FALSE))
out_long <- reshape2::melt(out_med)
pg_all$time <- out_long$Var2
pg_all$pred <- out_long$value
```

```{r }
attributes(projected$spatial_field)
out_med_sp <- apply(projected$spatial_field, c(1,3), median)
out_long_sp <- reshape2::melt(out_med_sp)
pg_all$sp_field <- out_long_sp$value
```

@@

  g
}

```{r}
median(pg_all$pred)
make_plot(pg_all, "pred") + facet_wrap(~ time) +
  scale_fill_gradient2(
    midpoint = median(pg_all$pred),
    low = scales::muted("blue"), 
    mid = "white",
    high = scales::muted("red"))

@@

make_plot(pg_all, "depth_scaled") +
  scale_fill_gradient2(
    midpoint = 0,
    high = scales::muted("blue"), 
    mid = "white",
    low = scales::muted("red"))
```
```
